---
title: "Events with contributions from the working group"
date: "Last change: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
bibliography: biblio.bib
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

## talks
path <- getwd()
talks <- as.data.frame(read_excel(paste(path, "/data/conferences.xlsx", sep = ""), col_types = NULL))
talks <- (talks %>% filter(is.na(Speaker1) == FALSE))
talks <- arrange(talks, desc(start_y), desc(start_m), desc(start_d))
talks$date <- with(talks, paste(ifelse(start_d < 10, paste("", start_d, sep = ""), start_d), ".", 
                                ifelse(start_m < 10, paste("", start_m, sep = ""), start_m), 
                                ".20", start_y, sep = ""))
```

# Upcoming events

-   12th December 2022: Together with ASA NJ chapter the WG is co-organizing a webinar [ASA New Jersey Chapter Webinar Series: Getting the question right: Applying the Estimand and Target Trial Frameworks with External Controls](communication/20221202_ASA_NJ_TTF_estimands.pdf).
-   29th-31st March 2023: Jonathan Siegel will give a presentation on estimands for time-to-event endpoints at the [Duke Industry Statistics Symposium 2023](https://sites.duke.edu/diss/).

# Past events

Below a list of past events with contributions of the WG, with links to slidedecks and recordings (where available).

```{r echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}

# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434

out1 <- NULL
for (i in 1:nrow(talks)){
  out1 <- c(out1, knit_expand('tools/conf1.Rmd'))
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```
