---
title: "Events"
date: "Last change: `r format(Sys.time(), '%d %B, %Y')`"
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
bibliography: biblio.bib
---

```{r setup, include = FALSE, echo = FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)

## talks
path <- getwd()
talks <- as.data.frame(read_excel(paste(path, "/data/conferences.xlsx", sep = ""), col_types = NULL))
talks <- (talks %>% filter(is.na(Speaker1) == FALSE))
```


# Upcoming events with contributions of the working group

* [ASA Biopharmaceutical Section Regulatory-Industry Statistics Workshop 2021](https://ww2.amstat.org/meetings/biop/2021)
  * _Clinical and Statistical Perspectives on Post-ICH E9 (R1) Addendum Estimand Use: Current Status and Future Directions_. Organizers: Kaspar Rufibach (Roche), Lei Nie (FDA), Shanti Gomatam (FDA). Frank Bretz (Novartis), Alexei Ionan (FDA). Presenters and panel discussion: Devan Mehrotra (Merck, ICH E9 (R1) Expert Working Group member, statistical), Sally Seymour (FDA, Division Director, clinical), David Lebwohl (Intellia Therapeutics, clinical), John Scott (FDA, CBER, statistical), Bohdana Ratitch (Bayer, statistical), Sylva Collins (FDA, CDER, statistical).
  * _Estimands in Oncology: White Papers from an Industry Working Group_. Organizer: Jonathan Siegel (Bayer). Presenters: Natalia Kan-Dobrosky (PPDI), Jonathan Siegel (Bayer), Satrajit Roychoudhury (Pfizer). Discussant: Qing Xu (FDA).

* [DIA webinar: Estimands How and Why - A Real Life Case Study in Oncology](https://diaglobal.zoom.us/webinar/register/WN_7KtHC7qtRRG78aJbZP9slg)
  * **Date and Time**: Sep 28th 2021, 10am - 11:30am EST
  * [**Registration**](https://diaglobal.zoom.us/webinar/register/WN_7KtHC7qtRRG78aJbZP9slg)
  * **Background**: The talk was previously presented in the European region (as part of a PSI webinar, [slides](talks/20210601_clin_eng.pdf) and [recording](https://www.psiweb.org/vod/item/psi-eiwg-webinar-estimands-in-oncology---how-and-why)) and received overwhelmingly positive feedback which motivated us to repeat this webinar and professional development opportunity in collaboration with the DIA Statistics and Data Science Community. 
  This time the webinar will include an extended 30 Minutes panel discussion.
  * **Panelists:** Lei Nie and Donna Przepiorka from FDA, Catherine Njue from Health Canada and Frank Bretz from Novartis.
  * **Description of the webinar:** The aim of estimand framework (the ICH E9 R1 guidance) is to increase the dialogue between functional areas working on proper alignment of trial objectives formulation, design, conduct, statistical analyses, and conclusions. This webinar is an opportunity to learn about the estimand framework. You will be guided through a case study (CheckMate 037) and interactively deepen the knowledge to gain hands-on experience in developing estimands. You will be introduced to the background and disease context of the case study, the concept of an estimand, and important clinical events that occurred in the trial and potentially affected interpretation of the results. Using non-technical language and clear graphical presentation of the concepts, you will experience how the estimand framework provides a common language to describe the diversity of patient journeys and why it is important to address the right question in clinical trials. The targeted learning outcomes are to 1) recognize the benefits of following the estimand framework (ICH E9 (R1) addendum) in the context of clinical trial setting, in order to have a common language to describe the diversity of patient journeys and address the right question in clinical trials; 2) be able to construct an estimand, including identification of relevant intercurrent events and application of relevant strategies to address them; and 3) gain insights from a cross-industry international working group on estimands in oncology.
  * **Target audience**: Clinicians, Investigators, Regulatory Experts, Medical Writers, Ethics Committees, and Statisticians. No need to have prior knowledge in oncology or of estimands.

# Past events and and all presentation slide decks

```{r echo = FALSE, message = FALSE, warning = FALSE, include = FALSE}

# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434

out1 <- NULL
for (i in 1:nrow(talks)){
  out1 <- c(out1, knit_expand('tools/conf1.Rmd'))
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
a <- knit(text = unlist(paste(out1, collapse = '\n')), quiet = TRUE)
```

```{r conferences, echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
cat(a)
```



