---
title: "Task forces"
date: last-modified
output: 
  rmarkdown::html_document:
    highlight: pygments
    number_sections: yes
    self_contained: yes
    toc: yes
    toc_depth: 3
    toc_float: yes
bibliography: biblio.bib
---

After a first phase where five subteams have written several publications (see [publications](publications.html)) the working group now operates within seven task forces. Objectives and member rosters of these task forces are available below.

```{r setup, include=FALSE}
## load packages
packs.html <- c("knitr", "pander", "reporttools", "dplyr", "readxl")
for (i in 1:length(packs.html)){library(packs.html[i], character.only = TRUE)}

knitr::opts_chunk$set(echo = TRUE)
panderOptions('table.alignment.default', function(df){ifelse(sapply(df, is.numeric), 'right', 'left')})

path <- getwd()

## =================================================================
## functions
## =================================================================
source(file = paste(path, "/tools/mydisp.r", sep = ""))
source(file = paste(path, "/tools/lead.r", sep = ""))
source(file = paste(path, "/tools/obj.r", sep = ""))

## =================================================================
## member list
## =================================================================
email <- as.data.frame(read_excel(paste(path, "/data/members.xlsx", sep = ""), col_types = NULL))
objectives <- as.data.frame(read_excel(paste(path, "/data/objectives.xlsx", sep = ""), col_types = NULL))
active <- objectives$active

## Current month
today <- Sys.Date()
tod <- format(today, format = "%d %B %Y")

## task forces
taskforces <- c("Clinical", "PS_switch", "PRO", "DOR", "FU", "RWD", "CondMarg", "T2E_sub", "early_dev_estimand_nexus", "Safety", "Switching", "Causal", "Censoring", "Solid", "Hematology")
taskforces_names <- c("Estimands engagement", "Principal stratification in clinical trials", "Patient-reported outcomes", "Duration of responses", "Quantification of follow-up", "Real-world data and estimands", "Conditional vs. marginal effects", "Time to event endpoints with prognostic or predictive biomarker subgroups", "Early development estimand nexus (EDEN)", "Estimands for Safety", "Treatment Switching", "Causal estimands", "Censoring", "Hematology", "Solid tumors")
```

# Task forces that are active and take new members

```{r, label = "activenew", echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out2 <- NULL
for (i in 1:length(taskforces)){
  
  if (active[i] == 2){
    out2 <- c(out2, knit_expand('tools/taskforce.Rmd'))
  }
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
cat(knit(text = unlist(paste(out2, collapse = '\n')), quiet = TRUE))
```

# Task forces that are active but do not take any new members

```{r, label = "active", echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out2 <- NULL
for (i in 1:length(taskforces)){
  
  if (active[i] == 1){
    out2 <- c(out2, knit_expand('tools/taskforce.Rmd'))
  }
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
cat(knit(text = unlist(paste(out2, collapse = '\n')), quiet = TRUE))
```

# Task forces or subteams that have concluded their work (apart from ongoing paper revisions)

```{r, label = "inactive", echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out2 <- NULL
for (i in 1:length(taskforces)){
  
  if (active[i] == 0){
    out2 <- c(out2, knit_expand('tools/taskforce.Rmd'))
  }
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
cat(knit(text = unlist(paste(out2, collapse = '\n')), quiet = TRUE))
```

```{r, label = "inactive_subteam", echo = FALSE, message = FALSE, warning = FALSE, results = "asis"}
# how to do this with child documents: https://gist.github.com/rmoff/a043676a2f084b81a434
out2 <- NULL
for (i in 1:length(taskforces)){
  
  if (active[i] == 3){
    out2 <- c(out2, knit_expand('tools/taskforce.Rmd'))
  }
}

# the "knit" command somehow produces unwanted output, this is why I assign its output to a and use a separate chunk to display a
cat(knit(text = unlist(paste(out2, collapse = '\n')), quiet = TRUE))
```




